\huge A Usability Evaluation of Tor Launcher

### 2017-03-03 pets2017-paper/pets2017-paper.tex
Edited the Cognitive Walkthrough section

\section{Cognitive Walkthrough}
\label{sec:inspection}
We inspected the interface to anticipate potential problems before testing it on real users.

@@

\begin{itemize}
\item {\bfseries Difficult tasks:} The interface uses technical and Tor-specific terms that are unfamiliar to an average user, such as the Tor network, internet service provider (ISP), local proxy, bridges, and transports. 
\item {\bfseries Too many choices:}  Users who do not need a bridge or proxy are able to configure them. There are nine choices for bridges by transport and more options to input a custom bridge. Almost any HTTP or SOCKS proxy can be used as the proxy. Custom bridge lines require the bridge information with specific syntax, but this syntax is not specified in the interface. Proxy fields also do not provide syntactic guidlines. See the whole list of possible errors in Appendix~\ref{states}. 
\item {\bfseries Poor feedback:} Even if there was a syntactic error in your bridge or proxy fields, it does not notifiy until a connection is made and fails. If a censored bridge was chosen, the connection timeout takes a over a couple minutes. Errors messages were often technical and did not give suggestions.
\end{itemize}

These are some of the factors that contributed to why users struggled with the interface and therefore were unable to connect to Tor quickly.

>>>>

\section{Cognitive Walkthrough}
\label{sec:inspection}
We inspected the interface to anticipate potential problems before testing it on study participants.

@@

\begin{itemize}
\item {\bfseries Difficult tasks:} The interface uses technical and Tor-specific terms that are likely to be unfamiliar to an average user, such as the Tor network, internet service provider (ISP), local proxy, bridges, and transports. 
\item {\bfseries Too many choices:}  Users who do not need a bridge or proxy are able to configure them. There are nine choices for bridges by transport and more options to input a custom bridge. Almost any HTTP or SOCKS proxy can be used as the proxy. Custom bridge lines require the bridge information with specific syntax, but this syntax is not specified in the interface. Proxy fields also do not provide syntactic guidelines. See the whole list of possible errors in Appendix~\ref{states}. 
\item {\bfseries Poor feedback:} Even if there was a syntactic error in the bridge or proxy fields, the user is not notified until after a connection is attempted and fails. If a censored bridge was chosen, the connection timeout takes several minutes. Error messages were often technical and did not give suggestions.
\end{itemize}

These are some of the factors that we believed contribute to users struggling with the interface and therefore may prevent them from connecting to Tor quickly.
